---
title: "Use Case A: Indirect effects of COVID-19 pandemic on vulnerable populations"
author: ""
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      out.width = "100%")
library(tidyverse)
library(readr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(plotly)
library(DT)
library(janitor)

```

## Use Case A on Vulnerable Populations ##
Wide variations in COVID-19 infection and outcomes exist across Europe and within countries. Use Case A explores the indirect impact of the pandemic on health care utilisation in three tracer groups of conditions - heart attack and stroke, hip and knee replacement and severe trauma. By incorporating deprivation measures, further comparisons examining differences across socioeconomic status can be investigated.


### LOCAL ANALYSES ###
This analyses corresponds with the local part of the analysis (country-specific). 
Please, provide feedback on your outputs, both data quality analysis (EDA), HTML report and aggregated output to the Use Case A leaders to complete the overall analyses.


</br>
</br>

```{r summary_proc , message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

age_max <- 105
age_diff <- 5
# years to plot (1 colored line per year)
year_from <- 2017
year_to <- 2020

date_from <- as.Date(paste0(year_from,'-01-01'))
date_to <- as.Date(paste0(year_to,'-12-31'))
# today
# today_y <- as.numeric(format(Sys.Date(), "%Y"))
# today_m <- as.numeric(format(Sys.Date(), "%m"))
# today_d <- as.numeric(format(Sys.Date(), "%d"))
# today_fractionalMonth <- today_m + today_d/as.numeric( as.Date(paste(today_y,today_m+1,"01", sep="-")) - as.Date(paste(today_y,today_m,"01", sep="-")) )


# Import synthetic data 
df <- read_delim("usecaseA_synthetic.csv", delim = "|", escape_double = FALSE, trim_ws = TRUE)

# df <- df %>% mutate(age_group = factor(cut(age_nm, seq(0, 109, 5), right = FALSE, 
#                         labels = c("0-4", "5-9", "10-14", "15-19", "20-24", 
#                                    "25-29", "30-34", "35-39", "40-44", "45-49",
#                                    "50-54", "55-59", "60-64", "65-69", "70-74",
#                                    "75-79", "80-84", "85-89", "90-94", "95-99", 
#                                    "99+")))) 

df <- df %>% mutate(age_group = cut(
  pmin(age_nm, age_max-1),
  seq(0, age_max, age_diff),
  right = FALSE,
  labels = c(
    paste(seq(0,age_max-2*age_diff,age_diff), seq(age_diff-1,age_max-age_diff-1,age_diff), sep="-"),
    paste(age_max-age_diff, "+", sep="")
    )
  ))


cohort1 <- df %>% filter(!is.na(date_event_heart) | !is.na(date_event_stroke) )  
cohort2 <- df %>% filter(!is.na(ttm_type_cd) , (!is.na(surgery_elective_hip) | !is.na(surgery_elective_knee)))  
cohort3 <- df %>% filter(!is.na(date_event) , !is.na(acute_event_trauma))  



year_months <- data.frame(
  month=rep(1:12, year_to-year_from+1),
  year= rep(year_from:year_to,each=12))

stroke_per_month_year <- cohort1 %>% 
  mutate(month = month(date_event_stroke), year = year(date_event_stroke)) %>% dplyr::select(year,month,patient_id) %>% 
  aggregate(.,by=list(.$year, .$month), FUN=length) %>% 
  transmute("year" = Group.1, "month" = Group.2, total_stroke = patient_id) 

stroke_per_month_year <- merge(year_months, stroke_per_month_year, by=c("year","month"),all.x = TRUE)
stroke_per_month_year[is.na(stroke_per_month_year)] <- 0

heart_per_month_year <- cohort1 %>% 
  mutate(month = month(date_event_heart), year = year(date_event_heart)) %>% dplyr::select(year,month,patient_id) %>% 
  aggregate(.,by=list(.$year, .$month), FUN=length) %>% 
  transmute("year" = Group.1, "month" = Group.2, total_heart_attack = patient_id) 

heart_per_month_year <- merge(year_months, heart_per_month_year, by=c("year","month"),all.x = TRUE)
heart_per_month_year[is.na(heart_per_month_year)] <- 0

knee_per_month_year <- cohort2 %>% filter(!is.na(surgery_elective_knee)) %>% 
  mutate(month = month(date_event), year = year(date_event)) %>% dplyr::select(year,month,patient_id) %>% 
  aggregate(.,by=list(.$year, .$month), FUN=length) %>% 
  transmute("year" = Group.1, "month" = Group.2, total_knee_replacement = patient_id) 

knee_per_month_year <- merge(year_months, knee_per_month_year, by=c("year","month"),all.x = TRUE)
knee_per_month_year[is.na(knee_per_month_year)] <- 0

hip_per_month_year <- cohort2 %>% filter(!is.na(surgery_elective_hip)) %>% 
  mutate(month = month(date_event), year = year(date_event)) %>% dplyr::select(year,month,patient_id) %>% 
  aggregate(.,by=list(.$year, .$month), FUN=length) %>% 
  transmute("year" = Group.1, "month" = Group.2, total_hip_replacement = patient_id) 

hip_per_month_year <- merge(year_months, hip_per_month_year, by=c("year","month"),all.x = TRUE)
hip_per_month_year[is.na(hip_per_month_year)] <- 0

acute_trauma_per_month_year <- cohort3 %>% 
  mutate(month = month(date_event), year = year(date_event)) %>% dplyr::select(year,month,patient_id) %>% 
  aggregate(.,by=list(.$year, .$month), FUN=length) %>% 
  transmute("year" = Group.1, "month" = Group.2, total_acute_trauma = patient_id) 

acute_trauma_per_month_year <- merge(year_months, acute_trauma_per_month_year, by=c("year","month"),all.x = TRUE)
acute_trauma_per_month_year[is.na(acute_trauma_per_month_year)] <- 0


summary_table <- merge(stroke_per_month_year, heart_per_month_year, by=c("year","month"),all.x = TRUE)
summary_table <- merge(summary_table, knee_per_month_year, by=c("year","month"),all.x = TRUE)
summary_table <- merge(summary_table, hip_per_month_year, by=c("year","month"),all.x = TRUE)
summary_table <- merge(summary_table, acute_trauma_per_month_year, by=c("year","month"),all.x = TRUE)
summary_table[is.na(summary_table)] <- 0

# 

dataset2 <- cohort1 %>% filter(!is.na(date_event_heart)) %>%
  mutate(month = month(date_event_heart), year = year(date_event_heart)) %>%  
  count(year,month,age_group,sex,socecon_lvl_cd) %>% rename(total_heart_attack = n )

dataset1 <-  cohort1 %>% filter(!is.na(date_event_stroke)) %>% 
  mutate(month = month(date_event_stroke), year = year(date_event_stroke)) %>%  
  count(year,month,age_group,sex,socecon_lvl_cd) %>% rename(total_stroke = n )

dataset3 <-  cohort2 %>% filter(!is.na(surgery_elective_knee)) %>% 
  mutate(month = month(date_event), year = year(date_event)) %>%  
  count(year,month,age_group,sex,socecon_lvl_cd) %>% rename(total_knee_replacement = n )

dataset4 <- cohort2 %>% filter(!is.na(surgery_elective_hip)) %>% 
  mutate(month = month(date_event), year = year(date_event)) %>%  
  count(year,month,age_group,sex,socecon_lvl_cd) %>% rename(total_hip_replacement = n )

dataset5 <-  cohort3 %>% 
  mutate(month = month(date_event), year = year(date_event)) %>%  
  count(year,month,age_group,sex,socecon_lvl_cd) %>% rename(total_acute_trauma = n )

summary_table_aggregated <- merge(x=dataset1,y=dataset2,by=c("year","month","age_group","sex","socecon_lvl_cd"),all=TRUE)
summary_table_aggregated <- merge(x=summary_table_aggregated,y=dataset3,by=c("year","month","age_group","sex","socecon_lvl_cd"),all=TRUE)
summary_table_aggregated <- merge(x=summary_table_aggregated,y=dataset4,by=c("year","month","age_group","sex","socecon_lvl_cd"),all=TRUE)
summary_table_aggregated <- merge(x=summary_table_aggregated,y=dataset5,by=c("year","month","age_group","sex","socecon_lvl_cd"),all=TRUE)
summary_table_aggregated[is.na(summary_table_aggregated)] <- 0


```

</br>
</br>

```{r plot1 , message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
month_breaks <- c(1,2,3,4,5,6,7,8,9,10,11,12)
month_names <-
  c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")


#############################################################################
#                             total_stroke                                    #
#############################################################################
p1<-ggplot(summary_table, aes(x=month, y=total_stroke, color = as.factor(year))) +
  geom_line(size = 1) +
  theme(panel.grid.major.x = element_line( color = "grey"),
        panel.grid.major.y = element_blank(), panel.border = element_blank(),
        panel.grid.minor = element_blank(), panel.background = element_blank(),
        axis.line = element_line(color = "black")) +
  theme(axis.text.x = element_text(angle = 90)) +
  geom_vline(xintercept = 3.76, color = "red", linetype = 2, size = 1) +
  labs(caption = paste0("n = ", sum(summary_table$total_stroke)),
       title = "Stroke", 
       color = "Year") +
  ylab(paste0("Absolute number of cases (N=", sum(summary_table$total_stroke),")")) +
  scale_x_continuous(name = "Month", breaks = month_breaks[1:12], labels = month_names, expand = c(0,0)) +
  theme(plot.subtitle = element_text(hjust = 1), plot.caption = element_text(hjust = 1))

ggplotly(p1)
```

</br>


```{r ratio_stroke}

highest_socecon_lvl <- max(df$socecon_lvl_cd)
highest_socecon_lvl <- `highest_socecon_lvl`




p1 <- 
  cohort1 %>% filter(!is.na(date_event_stroke), date_event_stroke >= date_from, date_event_stroke <= date_to) %>% 
  mutate(month = month(date_event_stroke), year = year(date_event_stroke)) %>% 
  group_by(year) %>%
  count(socecon_lvl_cd) %>%
  pivot_wider(id_cols = year, names_from = socecon_lvl_cd, values_from = n) %>%
  mutate(ratio = `1` / highest_socecon_lvl) %>% filter(!is.na(ratio)) %>% 
  ggplot(aes(x=year, y=ratio)) +
  geom_line(size=1) +
  geom_smooth(method = "loess") +
  theme(panel.grid.major.x = element_line( color = "grey"),
        panel.grid.major.y = element_blank(), panel.border = element_blank(),
        panel.grid.minor = element_blank(), panel.background = element_blank(),
        axis.line = element_line(color = "black")) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(title = "Ratio of most to least deprived (stroke)", 
       color = "Year") +
  # scale_x_continuous(name = "Year", breaks = month_breaks[1:12], labels = month_names, expand = c(0,0)) +
  theme(plot.subtitle = element_text(hjust = 1), plot.caption = element_text(hjust = 1))
  
ggplotly(p1)





```



</br>
</br>

```{r plot2 , message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
p1<-ggplot(summary_table, aes(x=month, y=total_heart_attack, color = as.factor(year))) +
  geom_line(size = 1) +
  theme(panel.grid.major.x = element_line( color = "grey"),
        panel.grid.major.y = element_blank(), panel.border = element_blank(),
        panel.grid.minor = element_blank(), panel.background = element_blank(),
        axis.line = element_line(color = "black")) +
  theme(axis.text.x = element_text(angle = 90)) +
  geom_vline(xintercept = 3.76, color = "red", linetype = 2, size = 1) +
  labs(subtitle = paste0("n = ", sum(summary_table$total_heart_attack)),
       title = "Heart attack", 
       color = "Year") +
  ylab(paste0("Absolute number of cases (N=", sum(summary_table$total_heart_attack),")")) +
  scale_x_continuous(name = "Month", breaks = month_breaks[1:12], labels = month_names, expand = c(0,0)) +
  theme(plot.subtitle = element_text(hjust = 1), plot.caption = element_text(hjust = 1))

ggplotly(p1)
```

</br>

```{r ratio_heart}


p1 <- 
  cohort1 %>% filter(!is.na(date_event_heart), date_event_heart >= date_from, date_event_heart <= date_to) %>% 
  mutate(month = month(date_event_heart), year = year(date_event_heart)) %>% 
  group_by(year) %>%
  count(socecon_lvl_cd) %>%
  pivot_wider(id_cols = year, names_from = socecon_lvl_cd, values_from = n) %>%
  mutate(ratio = `1` / highest_socecon_lvl) %>% filter(!is.na(ratio)) %>% 
  ggplot(aes(x=year, y=ratio)) +
  geom_line(size=1) +
  geom_smooth(method = "loess") +
  theme(panel.grid.major.x = element_line( color = "grey"),
        panel.grid.major.y = element_blank(), panel.border = element_blank(),
        panel.grid.minor = element_blank(), panel.background = element_blank(),
        axis.line = element_line(color = "black")) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(title = "Ratio of most to least deprived (heart attack)", 
       color = "Year") +
  # scale_x_continuous(name = "Year", breaks = month_breaks[1:12], labels = month_names, expand = c(0,0)) +
  theme(plot.subtitle = element_text(hjust = 1), plot.caption = element_text(hjust = 1))
  
ggplotly(p1)

```


</br>
</br>

```{r plot3 , message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
p1<-ggplot(summary_table, aes(x=month, y=total_knee_replacement, color = as.factor(year))) +
  geom_line(size = 1) +
  theme(panel.grid.major.x = element_line( color = "grey"),
        panel.grid.major.y = element_blank(), panel.border = element_blank(),
        panel.grid.minor = element_blank(), panel.background = element_blank(),
        axis.line = element_line(color = "black")) +
  theme(axis.text.x = element_text(angle = 90)) +
  geom_vline(xintercept = 3.76, color = "red", linetype = 2, size = 1) +
  labs(subtitle = paste0("n = ", sum(summary_table$total_knee_replacement)),
       title = "Knee replacement", 
       color = "Year") +
  ylab(paste0("Absolute number of cases (N=", sum(summary_table$total_knee_replacement),")")) +
  scale_x_continuous(name = "Month", breaks = month_breaks[1:12], labels = month_names, expand = c(0,0)) +
  theme(plot.subtitle = element_text(hjust = 1), plot.caption = element_text(hjust = 1))

ggplotly(p1)
```

</br>

```{r ratio_knee}



p1 <- 
  cohort2 %>% filter(!is.na(surgery_elective_knee), date_event >= date_from, date_event <= date_to)  %>% 
  mutate(month = month(date_event), year = year(date_event)) %>% 
  group_by(year) %>%
  count(socecon_lvl_cd) %>%
  pivot_wider(id_cols = year, names_from = socecon_lvl_cd, values_from = n) %>%
  mutate(ratio = `1` / highest_socecon_lvl) %>% filter(!is.na(ratio)) %>% 
  ggplot(aes(x=year, y=ratio)) +
  geom_line(size=1) +
  geom_smooth(method = "loess") +
  theme(panel.grid.major.x = element_line( color = "grey"),
        panel.grid.major.y = element_blank(), panel.border = element_blank(),
        panel.grid.minor = element_blank(), panel.background = element_blank(),
        axis.line = element_line(color = "black")) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(title = "Ratio of most to least deprived (knee replacement)", 
       color = "Year") +
  # scale_x_continuous(name = "Year", breaks = month_breaks[1:12], labels = month_names, expand = c(0,0)) +
  theme(plot.subtitle = element_text(hjust = 1), plot.caption = element_text(hjust = 1))
  
ggplotly(p1)

```


</br>
</br>

```{r plot4 , message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
p1<-ggplot(summary_table, aes(x=month, y=total_hip_replacement, color = as.factor(year))) +
  geom_line(size = 1) +
  theme(panel.grid.major.x = element_line( color = "grey"),
        panel.grid.major.y = element_blank(), panel.border = element_blank(),
        panel.grid.minor = element_blank(), panel.background = element_blank(),
        axis.line = element_line(color = "black")) +
  theme(axis.text.x = element_text(angle = 90)) +
  geom_vline(xintercept = 3.76, color = "red", linetype = 2, size = 1) +
  labs(subtitle = paste0("n = ", sum(summary_table$total_hip_replacement)),
       title = "Hip replacement", 
       color = "Year") +
  ylab(paste0("Absolute number of cases (N=", sum(summary_table$total_hip_replacement),")")) +
  scale_x_continuous(name = "Month", breaks = month_breaks[1:12], labels = month_names, expand = c(0,0)) +
  theme(plot.subtitle = element_text(hjust = 1), plot.caption = element_text(hjust = 1))

ggplotly(p1)
```

</br>

```{r ratio_hip}



p1 <- 
  cohort2 %>% filter(!is.na(surgery_elective_hip), date_event >= date_from, date_event <= date_to)  %>% 
  mutate(month = month(date_event), year = year(date_event)) %>% 
  group_by(year) %>%
  count(socecon_lvl_cd) %>%
  pivot_wider(id_cols = year, names_from = socecon_lvl_cd, values_from = n) %>%
  mutate(ratio = `1` / highest_socecon_lvl) %>% filter(!is.na(ratio)) %>% 
  ggplot(aes(x=year, y=ratio)) +
  geom_line(size=1) +
  geom_smooth(method = "loess") +
  theme(panel.grid.major.x = element_line( color = "grey"),
        panel.grid.major.y = element_blank(), panel.border = element_blank(),
        panel.grid.minor = element_blank(), panel.background = element_blank(),
        axis.line = element_line(color = "black")) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(title = "Ratio of most to least deprived (hip replacement)", 
       color = "Year") +
  # scale_x_continuous(name = "Year", breaks = month_breaks[1:12], labels = month_names, expand = c(0,0)) +
  theme(plot.subtitle = element_text(hjust = 1), plot.caption = element_text(hjust = 1))
  
ggplotly(p1)


```

</br>
</br>

```{r plot5 , message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}
p1<-ggplot(summary_table, aes(x=month, y=total_acute_trauma, color = as.factor(year))) +
  geom_line(size = 1) +
  theme(panel.grid.major.x = element_line( color = "grey"),
        panel.grid.major.y = element_blank(), panel.border = element_blank(),
        panel.grid.minor = element_blank(), panel.background = element_blank(),
        axis.line = element_line(color = "black")) +
  theme(axis.text.x = element_text(angle = 90)) +
  geom_vline(xintercept = 3.76, color = "red", linetype = 2, size = 1) +
  labs(subtitle = paste0("n = ", sum(summary_table$total_acute_trauma)),
       title = "Acute severe trauma", 
       color = "Year") +
  ylab(paste0("Absolute number of cases (N=", sum(summary_table$total_acute_trauma),")")) +
  scale_x_continuous(name = "Month", breaks = month_breaks[1:12], labels = month_names, expand = c(0,0)) +
  theme(plot.subtitle = element_text(hjust = 1), plot.caption = element_text(hjust = 1))

ggplotly(p1)


```

</br>

```{r ratio_accute}




p1 <- 
  cohort3 %>% filter(date_event >= date_from, date_event <= date_to) %>% 
  mutate(month = month(date_event), year = year(date_event))  %>% 
  group_by(year) %>%
  count(socecon_lvl_cd) %>%
  pivot_wider(id_cols = year, names_from = socecon_lvl_cd, values_from = n) %>%
  mutate(ratio = `1` / highest_socecon_lvl) %>% filter(!is.na(ratio)) %>% 
  ggplot(aes(x=year, y=ratio)) +
  geom_line(size=1) +
  geom_smooth(method = "loess") +
  theme(panel.grid.major.x = element_line( color = "grey"),
        panel.grid.major.y = element_blank(), panel.border = element_blank(),
        panel.grid.minor = element_blank(), panel.background = element_blank(),
        axis.line = element_line(color = "black")) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(title = "Ratio of most to least deprived (acute servere trauma)", 
       color = "Year") +
  # scale_x_continuous(name = "Year", breaks = month_breaks[1:12], labels = month_names, expand = c(0,0)) +
  theme(plot.subtitle = element_text(hjust = 1), plot.caption = element_text(hjust = 1))
  
ggplotly(p1)

```

</br>
</br>

### Summary table with total monthly cases by indicator ### 

```{r plottable , message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

datatable(summary_table, class = 'cell-border stripe')



```


```{r write_outputs , message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

write.csv(summary_table_aggregated, file = "aggregated_outputs.csv", row.names = FALSE)

```

