
---
title: "FAIR evaluation"
author: Document produced by HealthyCloud
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    number_section: yes
    theme: default
    toc: no
    toc_depth: 2
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(
  eval = TRUE,
	echo = TRUE,
	fig.align = "center",
	message = FALSE,
	warning = FALSE,
	fig.width=5.5,
	out.width = "100%"
)
# clean environment
rm(list=ls())
gc()
```

```{r, include=FALSE}

data_collection <- 'Give title to your data collection FAIR assessment'

findable_q1_title <- ''
findable_q2_title <- ''
findable_q3_title <- ''
findable_q4_title <- ''

q1_0 <- 'selected'
q1_a <- ''
q1_b <- ''
q1_c <- ''
q1_d <- ''

q2_0 <- 'selected'
q2_a <- ''
q2_b <- ''

q3_0 <- 'selected'
q3_a <- ''
q3_b <- ''
q3_c <- ''
q3_d <- ''

q4_0 <- 'selected'
q4_a <- ''
q4_b <- ''
q4_c <- ''
q4_d <- ''


```





```{r, include=FALSE}

if (file.exists("./FAIRevaluation.csv")) {

my_csv2 <- read.csv2(file = "./FAIRevaluation.csv", header=FALSE)

data_collection <- my_csv2[1]

findable_q1_title <- 'Do you have a unique identifier for your datasets?'
findable_q2_title <- 'Do you have a unique identifier for the metadata?'
findable_q3_title <- 'Do you produce or collect metadata for all your data (e.g. handbook, guide for users, description, keywords, timestamp, spatial coverage etc.)? Please specify'
findable_q4_title <- 'Do you have a public metadata catalogue service?'


if (my_csv2[21] == 'q1a') {q1_a <- 'selected'}
if (my_csv2[21] == 'q1b') {q1_b <- 'selected'}
if (my_csv2[21] == 'q1c') {q1_c <- 'selected'}
if (my_csv2[21] == 'q1d') {q1_d <- 'selected'}


if (my_csv2[22] == 'q2a') {q2_a <- 'selected'}
if (my_csv2[22] == 'q2b') {q2_b <- 'selected'}


if (my_csv2[23] == 'q3a') {q3_a <- 'selected'}
if (my_csv2[23] == 'q3b') {q3_b <- 'selected'}
if (my_csv2[23] == 'q3c') {q3_c <- 'selected'}
if (my_csv2[23] == 'q3d') {q3_d <- 'selected'}


if (my_csv2[24] == 'q4a') {q4_a <- 'selected'}
if (my_csv2[24] == 'q4b') {q4_b <- 'selected'}
if (my_csv2[24] == 'q4c') {q4_c <- 'selected'}
if (my_csv2[24] == 'q4d') {q4_d <- 'selected'}

}

```



# Data collection






<!-- jQuery (necessary for Bootstrap's JavaScript plugins)
<script src=https://ajax.googleapis.com/ajax/libs/jquery/1.11.1/jquery.min.js></script>
 -->

<!-- Bootstrap via CDN -->
<link rel=stylesheet href=https://maxcdn.bootstrapcdn.com/bootstrap/3.2.0/css/bootstrap.min.css>

<!-- Optional theme -->
<link rel=stylesheet href=https://maxcdn.bootstrapcdn.com/bootstrap/3.2.0/css/bootstrap-theme.min.css/>

<!-- Latest compiled and minified JavaScript -->
<script src=https://maxcdn.bootstrapcdn.com/bootstrap/3.2.0/js/bootstrap.min.js></script>


<style>
canvas {
-moz-user-select: none;
-webkit-user-select: none;
-ms-user-select: none;
}

.w3-container:after,.w3-container:before,.w3-panel:after,.w3-panel:before,.w3-row:after,.w3-row:before,.w3-row-padding:after,.w3-row-padding:before,
.w3-cell-row:before,.w3-cell-row:after,.w3-clear:after,.w3-clear:before,.w3-bar:before,.w3-bar:after{content:'';display:table;clear:both}
.w3-padding{padding:8px 0px!important}
.w3-green,.w3-hover-green:hover{color:#fff!important;background-color:#4CAF50!important}
.w3-border{border:1px solid #ccc!important}

.glyphicon-info-sign {font-size: 1.3em; color: #328cc7;}

a:link {color: #007B9A;}

a:visited {color: #007B9A;}
a {color: #007B9A;}

</style>

<script>

$('document').ready(initialise);
function initialise() {
$(document).on('change', 'select', function() {
update();
// if you want to do stuff based on the OPTION element:
//var opt = $(this).find('option:selected')[0];
});
update();
}


function update() {


var fscore = parseInt($('#q1').val()) + parseInt($("#q2").val()) + parseInt($('#q3').val()) + parseInt($('#q4').val());
$("#fbar").attr('style', "width: " +  (fscore / 17.0) * 100 + "%");
$("#fscore").html(parseInt((fscore / 17.0) * 100) + "%");
$("#fstars").html(createStars(fscore/17.0 * 5));

var ascore = parseInt($("#q5").val()) + parseInt($("#q6").val()) + parseInt($("#q7").val()) + parseInt($("#q14").val());
$("#abar").attr('style', "width: " +  (ascore / 10.0) * 100 + "%");
$("#ascore").html(parseInt((ascore / 10.0) * 100) + "%");
$("#astars").html(createStars(ascore/10.0 * 5));

var iscore = parseInt($("#q8").val()) + parseInt($("#q9").val()) + parseInt($("#q10").val());
$("#ibar").attr('style', "width: " +  (iscore / 8.0) * 100 + "%");
$("#iscore").html(parseInt((iscore / 8.0) * 100) + "%");
$("#istars").html(createStars(iscore/8.0 * 5));

var rscore = parseInt($("#q11").val()) + parseInt($("#q12").val()) + parseInt($("#q13").val());
$("#rbar").attr('style', "width: " +  (rscore / 7.0) * 100 + "%");
$("#rscore").html(parseInt((rscore / 7.0) * 100) + "%");
$("#rstars").html(createStars(rscore/7.0 * 5));

var tscore = fscore / 17 + ascore / 10.0 + iscore / 8.0 + rscore / 7.0;
$("#tbar").attr('style', "width: " +  tscore * 25.0 + "%");
$("#tscore").html(tscore);


$("#tpercentage").html(parseInt(tscore * 25.0) + "%");
console.log(tscore)
$("#tstars").html(createStars(tscore/4.0 * 5));

$("#q1_answer").html('<i>' + $("#q1 option:selected").text() + '</i>');
$("#q1_score").html($("#q1").val());

$("#q2_answer").html('<i>' + $("#q2 option:selected").text() + '</i>');
$("#q2_score").html($("#q2").val());

$("#q3_answer").html('<i>' + $("#q3 option:selected").text() + '</i>');
$("#q3_score").html($("#q3").val());

$("#q4_answer").html('<i>' + $("#q4 option:selected").text() + '</i>');
$("#q4_score").html($("#q4").val());

$("#f_total").html(fscore);

$("#q5_answer").html('<i>' + $("#q5 option:selected").text() + '</i>');
$("#q5_score").html($("#q5").val());

$("#q6_answer").html('<i>' + $("#q6 option:selected").text() + '</i>');
$("#q6_score").html($("#q6").val());

$("#q7_answer").html('<i>' + $("#q7 option:selected").text() + '</i>');
$("#7_score").html($("#q7").val());

$("#q14_answer").html('<i>' + $("#q14 option:selected").text() + '</i>');
$("#14_score").html($("#q14").val());

$("#a_total").html(ascore);

$("#q8_answer").html('<i>' + $("#q8 option:selected").text() + '</i>');
$("#q8_score").html($("#q8").val());
$("#q9_answer").html('<i>' + $("#q9 option:selected").text() + '</i>');
$("#q9_score").html($("#q9").val());
$("#q10_answer").html('<i>' + $("#q10 option:selected").text() + '</i>');
$("#q10_score").html($("#q10").val());
$("#i_total").html(iscore);

$("#q11_answer").html('<i>' + $("#q11 option:selected").text() + '</i>');
$("#q11_score").html($("#q11").val());
$("#q12_answer").html('<i>' + $("#q12 option:selected").text() + '</i>');
$("#q12_score").html($("#q12").val());
$("#q13_answer").html('<i>' + $("#q13 option:selected").text() + '</i>');
$("#q13_score").html($("#q13").val());
$("#r_total").html(rscore);


}

function createStars(score) {
var blank = '<span class="glyphicon glyphicon-star-empty" aria-hidden="true"></span>';
var filled = '<span class="glyphicon glyphicon-star" aria-hidden="true"></span>';
var html = "";
var i = 0;
score = Math.floor(score);

while (i < 5) {
if (score > i) {
html += filled;
} else {
html += blank;
}
i += 1;
}
return html;
}

</script>



<div class="container">




<div class="bs-example">
<div class="panel-group" id="accordion">
<form>
<input class="form-control" id="q0"  type="text"  name="q0" value="`r toString(data_collection)`" >
</form>
<BR>


This FAIR tool...


<!-- Findable -->
<div class="panel panel-default">
<div class="panel-heading">
<h4 class="panel-title">
<a data-toggle="collapse" href="#collapseOne">Findable</a>
<!--<a href="#fhelp" data-toggle="modal" data-target="#findable_info">
<span class="pull-right glyphicon glyphicon-info-sign"  aria-hidden="true">
</span>
</a>
-->
</h4>
</div>
<!--<div id="collapseOne" class="panel-collapse collapse in"> -->
<div id="collapseOne" class="panel-collapse collapse">
<div class="panel-body">
<form>

<!-- QUESTION Findable 1 -->
<div class="form-group row">
<label for="q1" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q1">

<!--Does the dataset have any identifiers assigned?
Do you have a unique identifier for your datasets? [C51]
-->
</a>

`r toString(findable_q1_title)`

</label>

<div class="col-sm-6">
<select class="form-control" id="q1" name="q1">

<!--
<option value="8">Globally Unique, citable and persistent (e.g. DOI, PURL, ARK
or Handle)
</option>
<option value="3">Web address (URL)</option>
<option value="1">Local identifier</option>
<option value="0" selected="selected">No identifier</option>
-->
<option id="q1-0" value="0" `r toString(q1_0)`>Do you have a unique identifier for your datasets?</option>
<option id="q1a" value="5" `r toString(q1_a)`>Yes (5)</option>
<option id="q1b" value="0" `r toString(q1_b)`>No (0)</option>
<option id="q1c" value="0" `r toString(q1_c)`>I don't know (0)</option>
<option id="q1d" value="0" `r toString(q1_d)`>This question doesn't apply to this data infrastructure (0)</option>

</select>
</div>
</div>

<!-- QUESTION Findable 2 -->
<div class="form-group row">
<label for="q2" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q2">

<!--Is the dataset identifier included in all metadata records/files describing the data?
Do you have a unique identifier for the metadata? [C53]-->

</a>

`r toString(findable_q2_title)`

</label>

<div class="col-sm-6">

<!--<select class="form-control" id="q2">
<option value="1">Yes</option>
<option value="0" selected="selected">No</option>
</select>-->
<select class="form-control" id="q2" name="q2">
<option id="q2-0" value="0" `r toString(q2_0)`>Do you have a unique identifier for the metadata?</option>
<option id="q2a" value="4" `r toString(q2_a)`>Yes (4)</option>
<option id="q2b" value="0" `r toString(q2_b)`>No (0)</option>
</select>


</div>
</div>

<!-- QUESTION Findable 3 -->
<div class="form-group row">
<label for="q3" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q3">

<!--How is the data described with metadata?
Do you produce or collect metadata for all your data (e.g. handbook, guide for users, description, keywords, timestamp, spatial coverage etc.)? Please specify. [C48]-->

</a>

`r toString(findable_q3_title)`

</label>

<div class="col-sm-6">
<!--<textarea>
<option value="4">Comprehensively (see suggestion) using a recognised formal machine-readable metadata schema.</option>
<option value="3">Comprehensively, but in a text-based, non-standard format.</option>
<option value="2">Brief title and description</option>
<option value="0" selected="selected">The data is not described</option>
</textarea>-->

<select class="form-control" id="q3" name="q3">
<option id="q3-0" value="0" `r toString(q3_0)`>Do you produce or collect metadata for all your data (e.g. handbook, guide for users, description, keywords, timestamp, spatial coverage etc.)?</option>
<option id="q3a" value="4" `r toString(q3_a)`>Comprehensively (see suggestion) using a recognised formal machine-readable metadata schema. (4)</option>
<option id="q3b" value="3" `r toString(q3_b)`>Comprehensively, but in a text-based, non-standard format. (3)</option>
<option id="q3c" value="2" `r toString(q3_c)`>Brief title and description (2)</option>
<option id="q3d" value="0" `r toString(q3_d)`>The data is not described (0)</option>

</select>
</div>
</div>


<!-- QUESTION Findable 4 -->
<div class="form-group row">
<label for="q4" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q4">

<!--What type of repository or registry is the metadata record in?
Do you have a public metadata catalogue service? [C50]-->

</a>

`r toString(findable_q4_title)`

</label>

<div class="col-sm-6">
<select class="form-control" id="q4" name="q4">

<!--<option value="4">Data is in one place but discoverable through several registries</option>
<option value="2">Generalist public repository</option>
<option value="2">Domain-specific repository</option>
<option value="2">Local institutional repository</option>
<option value="0" selected="selected">
The data is not described in any repository
</option>-->
<option id="q4-0" value="0" `r toString(q4_0)`>Do you have a public metadata catalogue service?</option>
<option id="q4a" value="4" `r toString(q4_a)`>Yes (4)</option>
<option id="q4b" value="0" `r toString(q4_b)`>No (0)</option>
<option id="q4c" value="0" `r toString(q4_c)`>I don't know (0)</option>
<option id="q4d" value="0" `r toString(q4_d)`>This question doesn't apply to this data infrastructure (0)</option>


</select>
</div>
</div>
</form>
<div class="w3-border">
<div id="fbar" class="w3-container w3-padding w3-green" style="width:0;">
<div class="w3-center" id="demo"></div>
</div>
</div>
</div>
</div>
</div>






<!-- Accessible -->
<div class="panel panel-default">
<div class="panel-heading">
<h4 class="panel-title">
<a data-toggle="collapse" href="#collapseTwo">Accessible</a>
<a href="#" data-toggle="modal" data-target="#accessible_info">
<span class="pull-right glyphicon glyphicon-info-sign" aria-hidden="true">
</span>
</a>
</h4>
</div>
<div id="collapseTwo" class="panel-collapse collapse">
<div class="panel-body">
<form>

<!-- QUESTION Accessible 1 -->
<div class="form-group row">
<label for="q5" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q5">

<!--How accessible is the data?-->
Do you provide access to individual and/or aggregated data (for third party users)? [C58]

</a>
</label>

<div class="col-sm-6">
<select class="form-control" id="q5" name="q5">

<!--<option value="5">Publicly accessible</option>
<option value="5">Fully accessible to persons who meet explicitly stated conditions,e.g. ethics approval for sensitive data</option>
<option value="4">A de-identified / modified subset of the data is publicly accessible</option>
<option value="3">Embargoed access after a specified date</option>
<option value="2">Unspecified conditional access e.g. contact the data custodian for access</option>
<option value="1">Access to metadata only</option>
<option value="0" selected="selected">No access to data or metadata</option>-->

<option value="4">Publicly accessible individual and aggregated (4)</option>
<option value="3">Publicly accessible aggregated (3)</option>
<option value="0" selected="selected">I don't know (0)</option>
<option value="0" selected="selected">This doesn't apply to this data infrastructure (0)</option>



</select>
</div>
</div>

<!-- QUESTION Accessible 2 -->
<div class="form-group row">
<label for="q6" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q6">

<!--Is the data available online without requiring specialised protocols or tools once access has been approved?-->
Is it possible to extract the data from the data infrastructure (e.g. download) or do they have to stay in the data infrastructure? [C62]

</a>
</label>

<div class="col-sm-6">
<select class="form-control" id="q6" name="q6">


<!--<option value="4">Standard web service API (e.g. OGC)</option>
<option value="3">Non-standard web service (e.g. OpenAPI/Swagger/informal API)</option>
<option value="2">File download from online location</option>
<option value="1">By individual arrangement</option>
<option value="0" selected="selected">No access to data</option>-->

<option value="4">Standard web service API (e.g. OGC) (4)</option>
<option value="3">Non-standard web service (e.g. OpenAPI/Swagger/informal API) (3)</option>
<option value="2">File download from online location (2)</option>
<option value="1">By individual arrangement (1)</option>
<option value="0" selected="selected">No access to data (0)</option>

</select>
</div>
</div>

<!-- QUESTION Accessible 3 -->
<div class="form-group row">
<label for="q7" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q7">

<!--Will the metadata record be available even if the data is no longer available?-->
Do third party users have to register to the data infrastructure and have an account in order to access the data? [C65]

</a>
</label>

<div class="col-sm-6">
<select class="form-control" id="q7" name="q7">

<!--<option value="1">Yes</option>
<option value="0">No</option>
<option value="0" selected="selected">Unsure</option>-->

<option value="1">Yes (1)</option>
<option value="0">No (0)</option>
<option value="0" selected="selected">Unsure (0)</option>

</select>
</div>
</div>



<!-- QUESTION Accessible 4 -->
<div class="form-group row">
<label for="q14" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q14">

<!--Will the metadata record be available even if the data is no longer available?-->
Are the conditions of access published? [C60]

</a>
</label>

<div class="col-sm-6">
<select class="form-control" id="q14" name="q14">

<option value="1">Yes (1)</option>
<option value="0">No (0)</option>
<option value="0" selected="selected">Unsure (0)</option>

</select>
</div>
</div>



</form>
<div class="w3-border">
<div id="abar" class="w3-container w3-padding w3-green" style="width:1%">
<div class="w3-center" id="idemo"></div>
</div>
</div>

</div>
</div>
</div>

<!-- Interoperable -->
<div class="panel panel-default">
<div class="panel-heading">
<h4 class="panel-title">
<a data-toggle="collapse" href="#collapseThree">Interoperable</a>
<a href="#" data-toggle="modal" data-target="#interoperable_info">
<span class="pull-right glyphicon glyphicon-info-sign"  aria-hidden="true">
</span>
</a>
</h4>
</div>
<div id="collapseThree" class="panel-collapse collapse">
<div class="panel-body">
<form>

<!-- QUESTION Interoperable 1 -->
<div class="form-group row">

<label for="q8" class="col-sm-6 col-form-label">
<a href="#reusable_info" data-toggle="modal" data-target="#info_q8">

<!--What (file) format(s) is the data available in?-->
What is the format(s) for distributing data? [C73] or [C25]

</a>
</label>

<div class="col-sm-6">
<select class="form-control" id="q8" name="q8">


<!--<option value="2">In a structured, open standard, machine-readable format</option>
<option value="1">In a structured, open standard, non-machine-readable format</option>
<option value="0" selected="selected">Mostly in a proprietary format</option>-->

<option value="4">In a structured, open standard, machine-readable format (csv, xml, json, R, ...)(4) </option>
<option value="2">In a structured, open standard, non-machine-readable format (2) (pdf)</option>
<option value="0" selected="selected">Mostly in a proprietary format (SAS) (0)</option>
<option value="0" selected="selected">Other (0)</option>
<option value="0" selected="selected">I don't know (0)</option>
<option value="0" selected="selected">This doesn't apply to this data infrastructure</option>


</select>
</div>
</div>

<!-- QUESTION Interoperable 2 -->
<div class="form-group row">
<label for="q9" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q9">

<!--What best describes the types of vocabularies/ontologies/tagging schemas used to define the data elements?-->
Which community-recognised vocabularies, standards or methodologies are used for metadata and data to facilitate interoperability? [C71]

</a>
</label>

<div class="col-sm-6">
<select class="form-control" id="q9" name="q9">


<!--<option value="3">Standardised open and universal using resolvable global identifiers linking to explanations</option>
<option value="2">Standardised vocabularies/ontologies/schema without global identifiers</option>
<option value="1">No standards have been applied in the description of data elements</option>
<option value="0" selected="selected">Data elements not described</option>-->

<option value="2">Standardised open and universal using resolvable global identifiers linking to explanations  (OPen ex: ...) (2)</option>
<option value="1">Standardised vocabularies/ontologies/schema without global identifiers (HL7, FHIR, SNOMED CT, LOINC, ICD-10,...) (1)</option>
<option value="1">Other (1)</option>
<option value="0" selected="selected">Data elements not described (0)</option>
<option value="0" selected="selected">I don't know (0)</option>
<option value="0" selected="selected">This doesn't apply to this data infrastructure (0)</option>

</select>
</div>
</div>

<!-- QUESTION Interoperable 3 -->
<div class="form-group row">
<label for="q10" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q10">

<!--How is the metadata linked to other data and metadata (to enhance context and clearly indicate relationships)?-->
Do you have a metadata record API endpoint (m2m) in place? [C75]

</a>
</label>

<div class="col-sm-6">
<select class="form-control" id="q10" name="q10">

<!--<option value="3">Metadata is represented in a machine readable format, e.g. in a linked data format such as Resource Description Framework (RDF).</option>
<option value="2">The metadata record includes URI links to related metadata, data and definitions</option>
<option value="0" selected="selected">There are no links to other metadata</option>-->

<option value="2">Yes (2)</option>
<option value="0" selected="selected">No (0)</option>
<option value="0" selected="selected">I don't know</option>
<option value="0" selected="selected">This question doesn't apply to this data infrastructure (0)</option>

</select>
</div>
</div>

<!-- Question removed...
<div class="form-group row">
<label for="q11" class="col-sm-6 col-form-label">
Does the metadata state how you wish your data to be cited?
</label>
<div class="col-sm-6">
<select class="form-control" id="q11">
<option value="1">Yes</option>
<option value="0" selected="selected">No</option>
</select>
</div>
</div>
-->

</form>
<div class="w3-border">
<div id="ibar" class="w3-container w3-padding w3-green" style="width:1%">
<div class="w3-center" id="iidemo"></div>
</div>
</div>


</div>
</div>
</div>

<!-- Reusable -->
<div class="panel panel-default">
<div class="panel-heading">
<h4 class="panel-title">
<a data-toggle="collapse" href="#collapseFour">Reusable</a>
<a href="#fhelp" data-toggle="modal" data-target="#reusable_info">
<span class="pull-right glyphicon glyphicon-info-sign"  aria-hidden="true">
</span>
</a>
</h4>
</div>
<div id="collapseFour" class="panel-collapse collapse">
<div class="panel-body">
<form>

<!-- QUESTION Reusable 1 -->
<div class="form-group row">
<label for="q11" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q11">

<!--Which of the following best describes the license/usage rights attached to the data?-->
Is there a clear procedure for third party users to request (the license) for data re-use? [C77]

</a>
</label>

<div class="col-sm-6">
<select class="form-control" id="q11" name="q11">

<!--<option value="4">Standard machine-readable license (e.g. Creative Commons)</option>
<option value="3">Standard text based license</option>
<option value="3">Non-standard machine-readable license(clearly indicating under what conditions the data may be reused)</option>
<option value="2">Non-standard text-based license</option>
<option value="0" selected="selected">No license</option>-->

<option value="3">Yes (3)</option>
<option value="0">No(0)</option>
<option value="0">I don't know (0)</option>
<option value="0" selected="selected">This question doesn't apply to this data infrastructure (0)</option>


</select>
</div>
</div>

<!-- QUESTION Reusable 2 -->
<div class="form-group row">
<label for="q12" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q12">

<!--How much provenance information has been captured to facilitate data reuse?-->
Have you placed the metadata related to your data infrastructure (that is, the above information provided in this survey) in another available source already? [C46]

</a>
</label>

<div class="col-sm-6">
<select class="form-control" id="q12" name="q12">

<!--<option value="3">Fully recorded in a machine readable format</option>
<option value="2">Fully recorded in a text format</option>
<option value="1">Partially recorded</option>
<option value="0" selected="selected">No provenance information is recorded</option>-->

<option value="2">Yes (2)</option>
<option value="0">No (0)</option>
<option value="1">I don't know (0)</option>
<option value="0" selected="selected">This question doesn't apply to this data infrastructure (0)</option>


</select>
</div>
</div>


<!-- QUESTION Reusable 3 -->
<div class="form-group row">
<label for="q13" class="col-sm-6 col-form-label">
<a href="#" data-toggle="modal" data-target="#info_q13">

<!--How much provenance information has been captured to facilitate data reuse?-->
Is it possible for third party users to access the data and re-use it for more than one purpose/project? [C76]

</a>
</label>

<div class="col-sm-6">
<select class="form-control" id="q13" name="q13">

<!--<option value="3">Fully recorded in a machine readable format</option>
<option value="2">Fully recorded in a text format</option>
<option value="1">Partially recorded</option>
<option value="0" selected="selected">No provenance information is recorded</option>-->

<option value="2">Yes (2)</option>
<option value="0">No (0)</option>
<option value="1">I don't know (0)</option>
<option value="0" selected="selected">This question doesn't apply to this data infrastructure (0)</option>


</select>
</div>
</div>



</form>
<div class="w3-border">
<div id="rbar" class="w3-container w3-padding w3-green" style="width:1%">
<div class="w3-center" id="rdemo"></div>
</div>
</div>


</div>
</div>
</div>
</div>

<h4>Total across F.A.I.R</h4>

<div class="w3-border">
<div id="tbar" class="w3-container w3-padding w3-green" style="width:0%">
<div class="w3-center" id="tdemo"></div>
</div>
</div>
<br>
<p>

  <form id="form">

<p> Stars <span id="tstars"></span></p>
<p> FINDABLE score <span id="fscore"></span></p>
<p> ACCESSIBLE score <span id="ascore"></span></p>
<p> INTEROPERABLE score <span id="iscore"></span></p>
<p> REUSABLE score <span id="rscore"></span></p>
<!--<p> FAIRNESS total score <span id="tscore"></span></p>-->
<p> FAIRNESS score <span id="tpercentage"></span></p>



<input class="form-control" type="hidden" id="findablescore" name="findablescore" value="" />
<input class="form-control" type="hidden" id="accessiblescore" name="accessiblescore" value="" />
<input class="form-control" type="hidden" id="interopscore" name="interopscore" value="" />
<input class="form-control" type="hidden" id="reusescore" name="reusescore" value="" />
<input class="form-control" type="hidden" id="totalscore" name="totalscore" value="" />

<input class="form-control" type="hidden" id="findable1" name="findable1" value="" />
<input class="form-control" type="hidden" id="findable2" name="findable2" value="" />
<input class="form-control" type="hidden" id="findable3" name="findable3" value="" />
<input class="form-control" type="hidden" id="findable4" name="findable4" value="" />



<input type="button" value="Download csv" id="dl" onclick="submitForm();">
</form>




```{r, echo=FALSE}


if (file.exists("./FAIRevaluation.csv")) {

library(dplyr)
library(ggplot2)


findable=c(as.integer(my_csv2[2])/17*100+ as.integer(my_csv2[3])/17*100+as.integer(my_csv2[4])/17*100+as.integer(my_csv2[5])/17*100,(17-as.integer(my_csv2[2])-as.integer(my_csv2[3])-as.integer(my_csv2[4])-as.integer(my_csv2[5]))/17*100)


df <- data.frame(
Findable = c("Findable", "Not findable"), value = findable)


bp<- ggplot(df, aes(x="", y=value, fill=Findable))+
geom_bar(width = 1, stat = "identity")+
  coord_fixed() +
xlab("") + 
ylab("")

pie <- bp + coord_polar("y", start=0,direction=-1) + ggtitle("Findable") + scale_fill_manual(values = c('blue','gray'))
plot(pie)

head(df)

}

```









```{r, echo=FALSE}


if (file.exists("./FAIRevaluation.csv")) {
  
findable=c(as.integer(my_csv2[2])/17*100, as.integer(my_csv2[3])/17*100,as.integer(my_csv2[4])/17*100,as.integer(my_csv2[5])/17*100,(17-as.integer(my_csv2[2])-as.integer(my_csv2[3])-as.integer(my_csv2[4])-as.integer(my_csv2[5]))/17*100)


df <- data.frame(
Findable = c("Do you have a unique identifier for your datasets?", "Do you have a unique identifier for the metadata?", "Do you produce or collect metadata for all your data?", "Do you have a public metadata catalogue service?",""), value = findable)


bp<- ggplot(df, aes(x="", y=value, fill=Findable))+
geom_bar(width = 1, stat = "identity")+
xlab("") + 
ylab("")

pie <- bp + coord_polar("y", start=0) + ggtitle("Findable")
plot(pie)

head(df)

}

```













<script>




//Clear form once submitted
function clearForm(){
document.getElementById("form").reset();
}



function submitForm() {

document.getElementById('findablescore').value= document.getElementById("fscore").textContent;
document.getElementById('accessiblescore').value= document.getElementById("ascore").textContent;
document.getElementById('interopscore').value= document.getElementById("iscore").textContent;
document.getElementById('reusescore').value= document.getElementById("rscore").textContent;
document.getElementById('totalscore').value= document.getElementById("tpercentage").textContent;

document.getElementById('findable1').value= q1[q1.selectedIndex].id;
document.getElementById('findable2').value= q2[q2.selectedIndex].id;
document.getElementById('findable3').value= q3[q3.selectedIndex].id;
document.getElementById('findable4').value= q4[q4.selectedIndex].id;



var formData = $("form").serializeArray();
let csv = "data:text/csv;charset=utf-8,"; // accept data as CSV

formData.forEach(function(item) {
csv += item.value + ";"; // concat form value on csv var and add ; to create columns (you can change to , if want)
});

var encodedUri = encodeURI(csv);

// if you want to download
var downloadLink = document.createElement("a");
downloadLink.setAttribute("download", "FAIRevaluation.csv");
downloadLink.setAttribute("href", encodedUri);
document.body.appendChild(downloadLink); // Required for FF
downloadLink.click();
downloadLink.remove();

clearForm();
}
</script>




 
</p>
</div>

</div>













<!-- Trigger the modal with a button
<button type="button" class="btn btn-info btn-lg" data-toggle="modal" data-target="#myModal">Open Modal</button>
-->

<!-- Modal -->
<div id="findable_info" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Findable</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="accessible_info" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Accessible</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="interoperable_info" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Interoperability</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="reusable_info" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Reusable</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q1" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About identifiers</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="info_q2" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About identifiers</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q3" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About metadata descriptions</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="info_q4" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About metadata repositories</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>



<div id="info_q5" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About data accessibility</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q6" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About protocols</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q7" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About metadata availability</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>





<div id="info_q8" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About file formats</h4>
</div>
<div class="modal-body">
 <p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="info_q9" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About schema standards</h4>
</div>
<div class="modal-body">
 <p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q10" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About metadata links</h4>
</div>
<div class="modal-body">
 <p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q11" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About licenses</h4>
</div>
<div class="modal-body">
 <p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="info_q12" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About provenance</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_q13" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">C76</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_fscore" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Findable Score</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="info_ascore" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Accessible Score</h4>
</div>
<div class="modal-body">
<p>.</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>


<div id="info_iscore" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modßal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Interoperable Score</h4>
</div>
<div class="modal-body">
<p>.
</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>

<div id="info_rscore" class="modal fade" role="dialog">
<div class="modal-dialog">

<!-- Modal content-->
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">About Reusable Score</h4>
</div>
<div class="modal-body">
 <p>.</p>
</div>
<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>

</div>
</div>



# Open-notebook
Access <A HREF=https://mybinder.org/v2/gh/Marine-Analyst/Jupyter/main?urlpath=rstudio TARGET=_blank>MyBinder.org/Marine-Analyst</A> virtual environment.<br>
More info at <A HREF=http://marine-analyst.eu/dev.py?N=50&O=487 TARGET=_blank>Marine-Analyst.eu</A><br>
<p xmlns:cc="http://creativecommons.org/ns#" >This document produced by <span property="cc:attributionName">Marine-analyst.eu</span> is licensed under <a href="http://creativecommons.org/licenses/by-nc/4.0/?ref=chooser-v1" target="_blank" rel="license noopener noreferrer" style="display:inline-block;">CC BY-NC 4.0<img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/cc.svg?ref=chooser-v1"><img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/by.svg?ref=chooser-v1"><img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/nc.svg?ref=chooser-v1"></a></p>

```{r, include=FALSE, results='hide'}
rm(list=ls())
gc()
```

